WWII Events Reduce Population in One Shanghai District While Increasing It in Others

### 2024-12-03 paper/paper.qmd
refined discussion section, added visualization

---
title: "WWII Events Reduce Population in One Shanghai District While Increasing It in Others"
subtitle: "Impact Analysis of Japanese Occupation on Population Shifts Across Shanghai’s Districts During WWII"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change"
date: today
date-format: long
abstract: "This paper evaluates the impact of three historic events on the population dynamics of Shanghai during WWII: the Japanese occupation of the Chinese-administered area, France’s surrender in WWII, and the Japanese occupation of the International Settlement. Data from the Virtual Shanghai research platform and historic publications are analyzed using a difference-in-difference model to estimate the effects of these events. The results indicate that the Japanese occupation of the Chinese-administered area led to an overall increase in Shanghai’s population across all districts. In contrast, France’s surrender during WWII had a negative impact on population numbers in all districts except the French Concession. Similarly, the Japanese occupation of the International Settlement caused population declines in all districts except the International Settlement itself. These findings underscore the complex demographic shifts resulting from geopolitical events and reveal how wartime occupation reshaped urban populations in uneven ways, reflecting resilience and displacement patterns."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

1940-06-22: France surrendered to Germany --\> French Concession stopped taking refugees

3\. 1942-01: Japanese armed forces claims authority over International Settlement (which was mainly under the governance of U.K and U.S prior to this date)

4\. 1945-08-15: Japan surrendered in WWII

5\. 1945-10: most Japanese armed forces withdrew from Shanghai

@@

knitr::kable(combined_data, col.names = c("Year", "Pop CHN District", "Pop IS", "Pop FC"), align = c("c", "c", "c", "c"))
```
This paper primarily evaluates three historic events between 1936 - 1942:
1. The Japanese occupation of Shanghai's Chinese-administrated District -- 1937-11-12
2. France surrendered to Germany -- 1940-06-22
3. Japanese armed forces claims authority over International Settlement -- 1942-01

@@

# Model

@@

### Model justification
The Difference-in-Difference model is chosen to evaluate the impact of historical events by comparing the observed outcomes, population changes, to an imaginary counterfactual scenario where these events did not occur.
The year variable captures the temporal trends, allowing the model to account for changes in population over time. The district variable identifies the three distinct regions in Shanghai (Chinese-administered district, International Settlement, and French Concession), each subject to unique governance and historical impacts. These inclusions enable the model to control for factors beyond the primary variables of interest (historical events).

@@

# Results
This section presents the population trends in Shanghai’s districts between 1936 and 1942, the estimated effects of district type and key historical events on population, and the district-specific impacts of these events as captured by interaction terms. The analysis highlights distinct population shifts driven by both district characteristics and the varying effects of war-related events.

## Population Trend
```{r}
#| label: fig-pop
#| fig-cap: Population in Shanghai between 1936 - 1942
#| echo: false
#| warning: false
#| message: false

# Create the bar chart with a trend line
ggplot(model_format, aes(x = year, y = population, fill = district_type, color = district_type)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +  # Bar chart with transparency
  geom_line(aes(group = district_type), size = 1) +  # Add trend line
  geom_point(size = 2) +  # Add points on the trend line
  scale_fill_brewer(palette = "Paired") +  # Use ColorBrewer palette for fill
  scale_color_brewer(palette = "Paired") +  # Use ColorBrewer palette for trend line
  labs(
    title = "Population In Shanghai between 1936-1942",
    x = "Year",
    y = "Population",
    fill = "District Type",
    color = "District Type"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    text = element_text(size = 12),
    plot.title = element_text(hjust = 0.5)
  )
```
The population trends from 1936 to 1942 reveal distinct shifts across the three districts in Shanghai: the Chinese-administered area, the French Concession, and the International Settlement. In the Chinese-administered area, the population remained stable until 1937, after which a decline began in 1940, continuing through 1942. The International Settlement experienced consistent population growth throughout the period, with the largest increases occurring after 1938. The French Concession maintained population stability until 1940, followed by a slight increase in 1941, which plateaued in 1942.

@@

knitr::kable(d_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c", "c"))
```
Model estimates highlight the influence of district type on population. The baseline population, Chinese-administrated district population, is represented by the intercept, is estimated at 11,792,816.58, with a standard error of 18,954,543.85. This estimate is not a realistic estimate since the year variable is not included. This intercept is population at year = 0, which does not actually exist. Temporal impact on population is estimated using the *year* variable, observing a decline of 59,841.02 across all districts, with a standard error of 98,298.59. The International Settlement exhibits a population difference of -943,281.63 (standard error: 381,299.41) compared to the Chinese-administered area, while the French Concession shows a difference of -1,642,126.91 (standard error: 350,808.44).

@@

knitr::kable(event_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c"))
```
The effects of three historical events on population are also quantified. The Japanese occupation of the Chinese-administered area in 1937 (cd_occupied) is associated with an increase of 89,350.01 (standard error: 350,665.57). France’s surrender in 1940 (french_surrender) results in a population decrease of 735,223.28 (standard error: 340,852.1). The Japanese occupation of the International Settlement in 1942 (is_occupied) corresponds to a population decrease of 88,982.32 (standard error: 361,506.9).

### Historic Events' Impact on Each District
```{r}
#| echo: false
#| eval: true
#| label: tbl-events_district
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

# Filter for the specific coefficient you want (e.g., "cd_occupied")
impact_types <- model_summary[8:12, ] |>
  mutate(estimate = round(estimate, 2),
    std.error = round(std.error, 2))

knitr::kable(impact_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c", "c", "c", "c"))
```
The interaction terms, which capture district-specific responses to historical events, provide additional insight. The Japanese occupation of the Chinese-administered area increases the population in the International Settlement by 89,430.69 (standard error: 414,726.8) and in the French Concession by 38,396.87 (standard error: 410,271.2). France’s surrender increases the population in the International Settlement by 470,617.65 (standard error: 352,215.9) and in the French Concession by 1,044,470.54 (standard error: 352,469.9). The Japanese occupation of the International Settlement itself is associated with an increase of 934,059.1 (standard error: 476,934.2) in the International Settlement’s population. Interaction terms differ from main effects by isolating the impact of historical events within each district type, providing a detailed analysis of population dynamics during this period.

# Discussion

## Interpretation of the Event Impacts
The results indicate that the Japanese occupation of the Chinese-administered area led to an overall increase in Shanghai’s population across all districts. In contrast, France’s surrender during WWII had a negative impact on population numbers in all districts except the French Concession. Similarly, the Japanese occupation of the International Settlement caused population declines in all districts except the International Settlement itself.

### Impact of Occupation in Chinese District
- By intuition, we would think that the foreign-force occupation of a district would lead to its population to fled to other areas. However, this does not seem the case for the Chinese-administrated District within Shanghai.
- This counter-intuitive phenomenon might be caused by several factors. 
Firstly, the increase in the districts population might be cause by an influx of foreign state refugees. Shanghai was, and still is, one of the largest economic center in China and has an abundance of non-land-dependent job opportunity. 战争时期，随时随地可能发生的战事极大的interrupted agriculture, subsequently leading to a large volume of unemployed farmers. These unemployed population will likely flood to economic centers and industrial center in search of a new job. (@sh, page 14)

### Impact of French Surrendering to Germany on Shanghai

### Impact of Occupation in International Settlement

## Reason why the French Concession was Exempted from Japanese Occupation

-   During WWII, on the European battlefield, France surrendered to Germany on June 22nd of 1940 (Check this & reference with a credible source). Since Japan was on the same side as Germany during that time, Japanese armed forces decided allow the French Concession to retain its own governance.
-   However, the French Concession is still constantly under the watch of the Japanese forces that has occupied the rest of Shanghai since 1942. 街上不得有侮辱日本的旗帜或者宣言，官方必须积极配合日本统治者进行有利于日本统治的宣传,etc.(can reference to video summary here)

## Refugees from outside of Shanghai Province

-   industrialization was not so popular back in the 1930s, many provinces are still mostly rural. But warfare messed with the land and the yields, causing many farmers to starve and ultimately have to seek refugee (find job) in industrialized city (where income is not dependent on land yield)
-   many people flooded to Shanghai for this reason (can insert calculation in data table 20 from reference book here)

### Job Oppurtunities in Shanghai

Aside from the instability caused by the Japanese armed forces, there are a few other reasons for Chinese population to move into the international settlement & French Concession. 1. Job opportunities - Heart of Shanghai city in the 1930-1940s, high pop density lead to boom of economy = more job opportunities - many factories are located with the settlements (less so in concession)

### Barrier to Entry in Job Market

2.  Barrier to Entry for certain job types

-   旧时候 -- 通讯还没有那么发达的时候，人们都很团结。那个时候同乡会的力量很强大。在外省，从同一个省来的漂泊者会互相帮扶着垄断一个城市的某种行业。例如，在旧上海，要做酒店生意的话你就必须是湖南人，给人做洗脚生意的肯定是苏北人。。。

@@

-   after the Japanese armed forces withdrawed from Shanghai, what follows is not recovery and rest for the local population
-   Competition for power within China's 2 political parties caused full-scale political warfare, now known as the *Chinese Civil War*
-   unlike Western political parties, Chinese political parties in the 1900s are more like parties of a throne. They each have their own ideology and an armed forces that follow. Most of all of the provinces are effected by this internal warfare, which ended in 1949 as 国民党 lost and withdrawed to Taiwan.

@@

### Data Measurement Weaknesses

-   data was recorded during wartime, many numbers were missing
-   base unit for population records is not ppl, it is instead "household". \# of ppl in a household is estimated based on historical data
-   many people chose to not report or partially report numbers due to convience or economic reasons, data may not be accurate

### Next Steps

@@

# Model details {#sec-model-details}
## Model Summary Table

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Complete Model Summary for DiD model used in analysis"
#| warning: false

modelsummary::modelsummary(
  list(
    "Population model" = did_model
  ),
  statistic = "mad",
  fmt = 2,
  metrics = c("R2", "RMSE")
)
```
\newpage

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

@@

@@

This appendix presents an idealized design for a population sampling survey, assuming that a data-recorder has unlimited time and authority to collect data within the historical timeframe of 1936–1942. The proposed methodology outlines a systematic approach to gathering detailed population data from Shanghai’s districts during pivotal wartime events, with considerations for the practical constraints and technology available during that period. While acknowledging the inherent challenges of conducting such a survey, this design aims to provide a comprehensive framework for understanding population dynamics within the Chinese-administered areas, International Settlement, and French Concession.

>>>>

---
title: "WWII Events Reduce Population in One Shanghai District While Increasing It in Others"
subtitle: "Impact Analysis of Japanese Occupation on Population Shifts Across Shanghai’s Districts During WWII"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change"
date: today
date-format: long
abstract: "This paper evaluates the impact of three historic events on the population dynamics of Shanghai during WWII: the Japanese occupation of the Chinese-administered area, France’s surrender in WWII, and the Japanese occupation of the International Settlement. Data from the Virtual Shanghai research platform and historic publications are analyzed using a difference-in-difference model to estimate the effects of these events. The results indicate that the Japanese occupation of the Chinese-administered area led to an overall increase in Shanghai’s population across all districts. In contrast, France’s surrender during WWII had a negative impact on population numbers in all districts except the French Concession. Similarly, the Japanese occupation of the International Settlement caused population declines in all districts except the International Settlement itself. These findings underscore the complex demographic shifts resulting from geopolitical events and reveal how wartime occupation reshaped urban populations in uneven ways, reflecting resilience and displacement patterns."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

3\. 1940-06-22: France surrendered to Germany --\> French Concession stopped taking refugees

4\. 1942-01: Japanese armed forces claims authority over International Settlement (which was mainly under the governance of U.K and U.S prior to this date)

5\. 1945-08-15: Japan surrendered in WWII

6\. 1945-10: most Japanese armed forces withdrew from Shanghai

@@

knitr::kable(combined_data, col.names = c("Year", "Pop CHN District", "Pop IS", "Pop FC"), align = c("c", "c", "c", "c"))
```

This paper primarily evaluates three historic events between 1936 - 1942: 1. The Japanese occupation of Shanghai's Chinese-administrated District -- 1937-11-12 2. France surrendered to Germany -- 1940-06-22 3. Japanese armed forces claims authority over International Settlement -- 1942-01

@@

# Model {#sec-model}

@@

### Model justification

The Difference-in-Difference model is chosen to evaluate the impact of historical events by comparing the observed outcomes, population changes, to an imaginary counterfactual scenario where these events did not occur. The year variable captures the temporal trends, allowing the model to account for changes in population over time. The district variable identifies the three distinct regions in Shanghai (Chinese-administered district, International Settlement, and French Concession), each subject to unique governance and historical impacts. These inclusions enable the model to control for factors beyond the primary variables of interest (historical events).

@@

# Results {#sec-results}

This section presents the population trends in Shanghai’s districts between 1936 and 1942, the estimated effects of district type and key historical events on population, and the district-specific impacts of these events as captured by interaction terms. The analysis highlights distinct population shifts driven by both district characteristics and the varying effects of war-related events.

## Population Trend

```{r, fig.pos="H"}
#| label: fig-pop
#| fig-cap: Population in Shanghai between 1936 - 1942
#| echo: false
#| warning: false
#| message: false

# Create the bar chart with a trend line
ggplot(model_format, aes(x = year, y = population, fill = district_type, color = district_type)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +  # Bar chart with transparency
  geom_line(aes(group = district_type), size = 1) +  # Add trend line
  geom_point(size = 2) +  # Add points on the trend line
  scale_fill_brewer(palette = "Paired") +  # Use ColorBrewer palette for fill
  scale_color_brewer(palette = "Paired") +  # Use ColorBrewer palette for trend line
  labs(
    title = "Population In Shanghai between 1936-1942",
    x = "Year",
    y = "Population",
    fill = "District Type",
    color = "District Type"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    text = element_text(size = 10),
    plot.title = element_text(hjust = 0.5)
  )
```

The population trends from 1936 to 1942 reveal distinct shifts across the three districts in Shanghai: the Chinese-administered area, the French Concession, and the International Settlement. In the Chinese-administered area, the population remained stable until 1937, after which a decline began in 1940, continuing through 1942. The International Settlement experienced consistent population growth throughout the period, with the largest increases occurring after 1938. The French Concession maintained population stability until 1940, followed by a slight increase in 1941, which plateaued in 1942.

@@

knitr::kable(d_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c", "c"))
```

Model estimates highlight the influence of district type on population. The baseline population, Chinese-administrated district population, is represented by the intercept, is estimated at 11,792,816.58, with a standard error of 18,954,543.85. This estimate is not a realistic estimate since the year variable is not included. This intercept is population at year = 0, which does not actually exist. Temporal impact on population is estimated using the *year* variable, observing a decline of 59,841.02 across all districts, with a standard error of 98,298.59. The International Settlement exhibits a population difference of -943,281.63 (standard error: 381,299.41) compared to the Chinese-administered area, while the French Concession shows a difference of -1,642,126.91 (standard error: 350,808.44).

@@

knitr::kable(event_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c"))
```

The effects of three historical events on population are also quantified. The Japanese occupation of the Chinese-administered area in 1937 (cd_occupied) is associated with an increase of 89,350.01 (standard error: 350,665.57). France’s surrender in 1940 (french_surrender) results in a population decrease of 735,223.28 (standard error: 340,852.1). The Japanese occupation of the International Settlement in 1942 (is_occupied) corresponds to a population decrease of 88,982.32 (standard error: 361,506.9).

### Historic Events' Impact on Each District

The interaction terms, which capture district-specific responses to historical events, provide additional insight. The Japanese occupation of the Chinese-administered area increases the population in the International Settlement by 89,430.69 (standard error: 414,726.8) and in the French Concession by 38,396.87 (standard error: 410,271.2). France’s surrender increases the population in the International Settlement by 470,617.65 (standard error: 352,215.9) and in the French Concession by 1,044,470.54 (standard error: 352,469.9). The Japanese occupation of the International Settlement itself is associated with an increase of 934,059.1 (standard error: 476,934.2) in the International Settlement’s population. Interaction terms differ from main effects by isolating the impact of historical events within each district type, providing a detailed analysis of population dynamics during this period.

```{r, fig.pos="H"}
#| label: fig-cd_occupied
#| fig-cap: Trend of Population after Chinese-administrated District became occupied in 1937
#| echo: false
#| warning: false
#| message: false

ggplot(model_format, aes(x = year, y = population, fill = district_type)) +
  geom_bar(stat = "identity") +  # Bar plot
  facet_wrap(~ district_type, strip.position = "bottom") +  # Facet by district_type
  geom_vline(xintercept = 1937, linetype = "dashed", color = "red") +  # Vertical dashed line
  geom_label(
    aes(
      x = 1939, y = 2500000,  # Adjust text position above 2,500,000
      label = "Starting from 1937,\nCHN District is occupied ---->"
    ),
    inherit.aes = FALSE,  # Prevent inheritance from aes()
    fill = "pink", color = "red", alpha = 0.3, size = 2.5, label.size = 0
  ) +
  # Add trend line for years >= 1937
  geom_smooth(
    data = model_format[model_format$year >= 1937, ],  # Filter data for years >= 1937
    aes(group = district_type),
    alpha = 0.8,
    method = "lm",  # Linear regression
    linetype = "dotted",
    color = "black", size = 1, se = FALSE  # Black trend line, no standard error
  ) +
  scale_y_continuous(limits = c(0, 2800000)) +  # Set y-axis limit to 2,800,000
  labs(
    title = "Population Trends after Occupation of CHN District",
    x = "Year",
    y = "Population",
    fill = "Year"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    legend.position = "bottom"
  )
```

```{r, fig.pos="H"}
#| label: fig-fr_surrender
#| fig-cap: Visualization of Population trend after French surrender in 1940
#| echo: false
#| warning: false
#| message: false

ggplot(model_format, aes(x = year, y = population, fill = district_type)) +
  geom_bar(stat = "identity") +  # Bar plot
  facet_wrap(~ district_type, strip.position = "bottom") +  # Facet by district_type
  geom_vline(xintercept = 1940, linetype = "dashed", color = "red") +  # Vertical dashed line
  geom_label(
    aes(
      x = 1939, y = 2500000,  # Adjust text position above 2,500,000
      label = "Starting from 1940, \nFrance surrendered to Germany -->"
    ),
    inherit.aes = FALSE,  # Prevent inheritance from aes()
    fill = "lightgreen", color = "black", alpha = 0.3, size = 2, label.size = 0
  ) +
  # Add trend line for years >= 1937
  geom_smooth(
    data = model_format[model_format$year >= 1940, ],  # Filter data for years >= 1937
    aes(group = district_type),
    alpha = 0.8,
    method = "lm",  # Linear regression
    linetype = "dotted",
    color = "black", size = 1, se = FALSE  # Black trend line, no standard error
  ) +
  scale_y_continuous(limits = c(0, 2800000)) +  # Set y-axis limit to 2,800,000
  labs(
    title = "Population Trend After French Surrender",
    x = "Year",
    y = "Population",
    fill = "Year"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    legend.position = "bottom"
  )
```

# Discussion {#sec-discussion}

The results highlight the varying population shifts in Shanghai’s three districts during key historical events in WWII. The Japanese occupation of the Chinese-administered district led to an overall increase in Shanghai’s population across all districts. In contrast, France’s surrender during WWII negatively impacted population numbers in all districts except the French Concession. Similarly, the Japanese occupation of the International Settlement caused population declines in all districts except the International Settlement itself.

## Occupation in Chinese District

Contrary to expectations, the Japanese occupation of the Chinese-administered district did not result in population declines. Instead, this district experienced an increase in population, likely driven by refugees fleeing rural provinces. The devastation of agricultural economies due to ongoing warfare forced farmers to seek alternative livelihoods in urban centers. Shanghai, being an economic hub with abundant industrial job opportunities, became a natural destination for displaced populations (@sh, page 14).

Industrialization during the 1930s and 1940s was concentrated in cities like Shanghai, while most provinces remained predominantly rural. Disrupted farming activities caused widespread unemployment, prompting many to migrate to Shanghai, where income was not tied to land productivity. The high population density in Shanghai further fueled its economic growth, offering a range of job opportunities, especially in manufacturing industries located in the foreign settlements.

However, access to jobs was not uniform. Historical records suggest that certain industries were dominated by migrants from specific provinces due to the strong influence of regional associations. For example, hotel businesses were often monopolized by individuals from Hunan, while the footbath service industry was controlled by migrants from Northern Jiangsu. This social network-based hiring created barriers to entry for outsiders, shaping the employment landscape in Shanghai.

## French Surrendering to Germany on Shanghai Population

The French Concession displayed unique population dynamics during WWII. Following France’s surrender to Germany on June 22, 1940, the concession ceased accepting refugees. This sudden shift in refugee policy aligns with geopolitical developments, as France temporarily allied with Germany during this period. The Japanese armed forces allowed the French Concession to maintain governance autonomy, likely due to this alliance.

Despite retaining governance, the French Concession operated under the watchful eye of Japanese forces, who occupied the rest of Shanghai by 1942. Compliance with Japanese regulations, including bans on anti-Japanese propaganda, was mandatory. The political alignment with Germany thus shielded the French Concession from direct occupation but altered its role as a haven for refugees.

## Occupation in International Settlement
The Japanese occupation of the International Settlement resulted in a population pattern contrary to initial expectations. While occupation typically drives residents away, the settlement remained one of the safest and most expensive areas in Shanghai. With the French Concession no longer accepting refugees, the International Settlement became the primary refuge for displaced individuals, stabilizing its population despite foreign control. Its status as an elite residential district further insulated it from severe population declines.

@@

The end of Japanese occupation in 1945 did not bring stability to Shanghai. Instead, the city became embroiled in the Chinese Civil War, as the two dominant political parties—Kuomintang and the Chinese Communist Party—vied for control. Unlike Western political parties, these factions operated as militarized entities with distinct ideologies and armed forces. The civil war, which engulfed much of China, ended in 1949 with the Kuomintang retreating to Taiwan, leaving behind a landscape marked by prolonged instability.

@@

The study acknowledges several limitations. First, data recorded during wartime is incomplete, with many population figures missing. Additionally, population counts were based on households, with the number of individuals per household estimated from historical averages. This approach may not accurately capture the actual population. Furthermore, under-reporting or partial reporting for economic or convenience reasons may have compromised data accuracy.

Future research should focus on improving data reconstruction methods, incorporating archival records, and leveraging advanced modeling techniques to address these limitations. Expanding the analysis to include other affected regions in China could also provide a broader understanding of the population dynamics during WWII.

@@

# Model details {#sec-model-details}

@@

```{r, fig.pos="H"}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

```{r, fig.pos="H"}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

@@

## Model Summary
```{r, fig.pos="H"}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Complete Model Summary for DiD model used in analysis"
#| warning: false

modelsummary::modelsummary(
  list(
    "Population model" = did_model
  ),
  statistic = "mad",
  fmt = 2,
  metrics = c("R2", "RMSE")
)

```
\newpage

@@

This appendix presents an idealized design for a population sampling survey, assuming that a data-recorder has unlimited time and authority to collect data within the historical time-frame of 1936–1942. The proposed methodology outlines a systematic approach to gathering detailed population data from Shanghai’s districts during pivotal wartime events, with considerations for the practical constraints and technology available during that period. While acknowledging the inherent challenges of conducting such a survey, this design aims to provide a comprehensive framework for understanding population dynamics within the Chinese-administered areas, International Settlement, and French Concession.
